\documentclass{resume} % Add 'print' for b/w

\begin{document}

\header
{Joseph }
{Curtis}
{Nuclear Engineer}
{Radiation Detection \space \faPlusSign \space\space Data Analysis \space \faPlusSign \space\space Modeling \& Simulation}
{1526 Arch St Apt 4 Berkeley, CA 94708, USA\space\space\faHome}
{\href{mailto:joseph.c.curtis@gmail.com}{joseph.c.curtis@gmail.com}\space\space\faEnvelopeAlt}
{(831) 277 6231\space\space\faPhone}
{\href{http://jccurtis.github.io}{jccurtis.github.io}\space\space\faGithub}
{\href{http://www.linkedin.com/in/josephccurtis}{josephccurtis}\space\space\faLinkedinSign}

\section{education}
\begin{entrylist}
	\entry
		{2012--2014 (Fall)}
		{Masters of Science {\normalfont Nuclear Engineering (GPA 3.84)}}
		{University of California, Berkeley}
		{
		\emph{Benchmarking the Gamma Ray Sensors on RadMAP}
		}
	\entry
		% the Berkeley Radiological Air and Water Monitoring Project
		{2007--2011}
		{Bachelor of Science {\normalfont Nuclear Engineering (GPA 3.86)}}
		{University of California, Berkeley}
		{
		\emph{Honors Thesis: Measurements and Analysis of Fukushima Fallout by BRAWM}
		}
\end{entrylist}

\section{awards}
\begin{entrylist}
	\entrymin
		{2014}
		{Member of Alpha Nu Sigma}
		{American Nuclear Society Honor Society}
	\entrymin
		% Awarded to one graduate student instructor as elected by department faculty and approved by UC Berkeley.
		{2013}
		{Outstanding Graduate Student Instructor}
		{Graduate Division, UC Berkeley}
		%\entrymin
		%{2011}
		%{Graduated with High Honors}
		%{College of Engineering, UC Berkeley}
	\entrymin
		{2011}
		{Departmental Citation (Top GPA in graduating class)}
		{Dept of Nuclear Engineering, UC Berkeley}
	\entrymin
		{2009}
		{The Virgil Schrock Scholarship}
		{Dept of Nuclear Engineering, UC Berkeley}
	\entrymin
		{2009}
		{Member of Tau Beta Pi}
		{National Engineering Honor Society}
\end{entrylist}

\section{experience}
\begin{entrylist}
	\entry
		{Jan `15 -- Present}
		{Associate Specialist}
		{Lawrence Berkeley National Laboratory}
		{
		Upgrading hardware and real-time analysis software on mobile radiation detection system (RadMAP).
		}
	\entry
		{Aug `12 -- Dec `14}
		{Graduate Student Researcher}
		{Lawrence Berkeley National Laboratory}
		{
		Experimentally validated Monte-Carlo and ray-tracing gamma-ray physics simulations.
		}
	\entry
		% Kai Vetter, Sahak M
		% Entrusted with experimental setup for graduate level laboratory course. Advanced Concepts In  Supported course experiments with coding, designing, machining and teaching. Performed experimental setup for graduate radiation detection laboratory course.
		{Aug `11 -- Aug `12}
		{Junior Specialist}
		{Dept of Nuclear Engineering, UC Berkeley}
		{
		Supported graduate radiation laboratory course with signal processing coding, machining and teaching.%
		}
	\entry
		% Kai Vetter, Mark Bandstra
		% Coordinated sample purchasing, collection, preparation and HPGe spectroscopic measurement for air, water and food samples to monitor for fallout particles from the Fukushima Dai-ichi Reactor incident. Performed analysis of radionuclide ratios in comparison with modeled release ratios from the Japanese reactors.
		{Mar `11 -- May `11}
		{Honor's Research Assistant}
		{Dept of Nuclear Engineering, UC Berkeley}
		{
		Analyzed environmental samples for Fukushima Daiichi Reactor fallout monitoring.%
		%HPGe spectroscopic measurement for air, water and food samples to monitor for fallout particles from the Fukushima Dai-ichi Reactor incident. Performed analysis of radionuclide ratios in comparison with modeled release ratios from the Japanese reactors.
		}
	\entry
		%Teamed with fellow student to develop five digital-domain radiation detection experiments using HPGe, CZT, NaI(Tl) and liquid scintillation detectors. Composed MATLAB codes for data post-processing. Assembled PopTop HPGe detector. Taught lab section at Summer School in Radiation Detection and Measurement (SSRDM, UC Berkeley and University of Tokyo.) Assisted development and execution of five digital-domain radiation detection experiments.
		{Jun `10 -- Aug `10}
		{Lab Technician \& Instructor}
		{UC Berkeley \& University of Tokyo}
		{
		Trained students from the United States and Japan to perform digital radiation detection experiments.%
		}
	\entry
		% Ed Blanford, Per Peterson
		% Designed and experimentally verified a first order fluid mechanics model in MATLAB. Developed the laboratory’s academic research website. Upgraded photo-gate sensors with amplifier circuits.
		{Jan `09 -- Dec `09}
		{Thermo-Hydraulics Research Assistant}
		{University of California, Berkeley}
		{
		Designed and experimentally verified a first order fluid mechanics model in MATLAB.
		}
	\entry
		% Steve Andrews
		% Tested GPS equipment by driving a rental car during rush hour in order to gather traffic data for study.
		{Jan `09 -- May `09}
		{Field Tester}
		{California Center for Innovative Transportation}
		{
		Aggregated real-time traffic data with cell phone based GPS equipment by driving a test vehicle.%
		}
\end{entrylist}

\section{leadership}
\begin{entrylist}
	\entry
		% (radwatch.berkeley.edu/dosenet) Software and Hardware development  
		{2015 -- Present}
		{DoseNet Project Co-lead}
		{Dept of Nuclear Engineering, UC Berkeley}
		{
		Managing technical development of networked radiation sensors for educational outreach. 
		}
	\entry
		{2009 -- 2014}
		{Engineering for Kids Day (E4K)}
		{College of Engineering, UC Berkeley}
		{
		Coordinated logistics and safety for 300+ children during annual engineering outreach program.
		}
	\entry
		{2012 -- 2013}
		{Head Graduate Student Instructor}
		{Dept of Nuclear Engineering, UC Berkeley}
		{
		Led three other instructors to setup, conduct, teach and assess undergraduate course experiments.
		}
	\entry
		{2008 -- 2011}
		{American Nuclear Society}
		{Student Chapter, UC Berkeley}
		{
		Managed operations, organized outreach and liaised with national chapter as secretary, vp and president.%
		}
	\entry
		{2009 -- 2010}
		{Engineers Joint Council}
		{College of Engineering, UC Berkeley}
		{
		Facilitated annual budget allocation of college-wide funding for engineering student groups.
		}
	\entry
		{2009}
		{Tau Beta Pi}
		{Student Chapter, UC Berkeley}
		{
		Managed external relations with other student societies to foster collaborative relationships.
		}
\end{entrylist}

\section{skills}
\textbf{Programming:} Python, MATLAB, git, Bash, HDF5, SLURM, \LaTeX, CSS \& HTML\\
\textbf{Techniques:} Scalable high performance computing, Monte-Carlo methods, uncertainty analysis, gamma-ray spectroscopy

%\section{interests}
%
%\textbf{professional:} big data analysis, monte carlo simulations, machine learning, medical imaging technologies\\\textbf{personal:} photography, rock climbing, backpacking, cycling, open source coding

%----------------------------------------------------------------------------------------

\end{document}
